Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-17 appendix.qmd
Updated PBMC3k data section

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a, and two views of the fit in projections from $50\\text{-}D$, for the PBMC data ($n =  5858$ and $p = 50$). Layout shows close clusters. In $50\\text{-}D$, the data shows "
#| label: fig-model-pbmc-author-proj-scdeed
#| fig-pos: H
#| fig-width: 15
#| fig-height: 5
#| out-width: 30%

>>>>

```{r}
#| echo: false
#| eval: false
#| fig-cap: "Model in \\gD{}, on the layout a, and two views of the fit in projections from $50\\text{-}D$, for the PBMC data ($n =  5858$ and $p = 50$). Layout shows close clusters. In $50\\text{-}D$, the data shows "
#| label: fig-model-pbmc-author-proj-scdeed
#| fig-pos: H
#| fig-width: 15
#| fig-height: 5
#| out-width: 30%
